Meta-analysis of the Interoceptive Accuracy Scale (IAS) Structure and its Subjective Correlates

### 2024-11-17 paper/1_Initial/manuscript.qmd
removes notes (now int able)

Our search focused on studies citing the original IAS validation paper [@murphy2019], identifying 136 papers (as of **XX/XX/2024**).
To qualify for inclusion, papers needed to (1) provide accessible data in open-access, (2) employ the IAS as a measure, and (3) report individual IAS items scores.
A total of 9 studies was included.
Additionally, we added datasets of two unpublished (but already open-access) studies from our lab.
See @tbl-samples for a summary of the samples demographics.

@@

**Note**.
\* Numbers were sourced from the original paper rather than independently calculated.
\*\* Data for Makowski et al., 2023a: <https://raw.githubusercontent.com/RealityBending/IllusionGameReliability/main/data/preprocessed_questionnaires.csv> and Makowski et al., 2013b: <https://raw.githubusercontent.com/DominiqueMakowski/PHQ4R/main/study2/data/data.csv>

@@

The analysed sample contains 31,317 participants, of which 71.5% are females.

>>>>

Our search focused on studies citing the original IAS validation paper [@murphy2019], identifying 136 papers (as of **XX/XX/2024**).
To qualify for inclusion, papers needed to (1) provide accessible data in open-access, (2) employ the IAS as a measure, and (3) report individual IAS items scores.
A total of **XX** studies was included.
We also included the data of two unpublished (but already open-access) studies from the authors.
The total N participants was 31,317 participants (Mean SD, 71.5% Female).
See @tbl-samples for a summary of the samples demographics.

@@

@@
